TacticToe: Learning the Game of Tactics

### 2018-02-15 tactictoe_jv.tex
examples wip

In Example~\ref{ex:cs3}, we prove a theorem about lists which is domain where 
\tactictoe excels compared to ATPs. 
Given two list $l1$ and $l2$ where the length of $l1$ is less than a natural 
number $n$, the theorem states that performing an update on the $n^{th}$ 
element of the concatenation of $l1$ and $l2$ is the same as
performing an update on the $m^{th}$ element of $l2$ where $m = n - 
\mathit{length} l1$ followed by concatenation. Again, \tactictoe's proof is 
much more readable starting with applying induction on $l$. It solves the base 
case of the induction by rewriting and distinguish cases where $n=0$ or $n>0$ 
in the inductive hypothesis. It finalizes the proof using the definition of 
$LUPDATE$. Here, \tactictoe's proof is arguably smaller, faster and easier to 
understand and maintain. Such proofs after an expert review could replace the 
original human proofs in the \holfour repository.

>>>>

In Example~\ref{ex:cs3}, we prove a theorem about lists which is domain where 
\tactictoe excels compared to ATPs. 
Given two list $l_1$ and $l_2$ where the length of $l_1$ (noted $p$) is less 
than a natural 
number $n$, the theorem states that performing an update on the $n^{th}$ 
element of the concatenation of $l_1$ and $l_2$ is the same as
performing an update on the $m^{th}$ element of $l_2$ where $m = n - p$. Again, 
\tactictoe's proof is 
much more readable starting with applying induction on $l$. It solves the base 
case of the induction by rewriting and distinguish cases where $n=0$ or $n>0$ 
in the inductive hypothesis. It finalizes the proof using the definition of 
$LUPDATE$. Here, \tactictoe's proof is arguably smaller, faster and easier to 
understand and maintain. Such proofs after an expert review could replace the 
their respective original human proofs in the \holfour repository.
